New results in $\sfrac{k}{n}$ Power-Hours

### 2013-12-28 powerhour/paper/paper.tex
Sync metroid. 1D grid rendering (old), some work on paper and sampler (new)

Now we execute programs as before, and hope that we never encounter a
situation where we depend on a rule. If we finish without ever using
one of the \any\ rules, we evaluated a potentially large group of
configurations all at once. During the execution of a configuration,
if we need to use a rule that is currently marked \any, we explore all
of the possibilities. This is accomplished by a loop that looks like
the following (in Pseudo SML):

@@

% XXX TODO: Display in 3D cube.
It is also feasible overnight to enumerate all three-player games. The
results are three-dimensional, of course, but we can display the
outcomes for two of the players in the familiar presentation
(Figure~\ref{cig:3and2}). Note that $\langle k_1, k_2, k_3 \rangle$ is
achievable for any $k_1$, $k_2 \in \{ 0, 1, 2 \}$, and some unknown
$k_3$ (projected out of this display). This is a significant
improvement over what was achievable in BMML with two players. It
suggests that with enough friends willing to follow a program, some
set of people are likely to be able to achieve any amount of drinks
between them (if they have the ability to construct the right rule
set!); see Section~\ref{sec:conjectures}.

The sheer number of configurations for 4 or more players makes these
exact enumeration techniques infeasible. However, we have other
avenues for generalization (and exploration), which are explored in
the next chapter.

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.90 \linewidth]{soloncups.pdf}
\end{center}\vspace{-0.1in}
\caption{Possible outcomes for BM$n$L with a single player. With no
  cup states, it is only possible to drink nothing. By convention, the
  0\th\ cup is the special ``filled'' state, so it is only possible to
  drink on every turn (60) or never (0). As we add more cup states,
  the number of achievable states strictly increases; with 8 cup states
  we can drink any amount. 7 and 53 drinks are the most difficult to
  achieve, and can only be done with 8 cup states.
}
\label{fig:soloncups}
\end{figure}

@@

\begin{enumerate}
  \item With one player, we have exact bounds on what is possible in
    the generalized case. With 8 cup states, a single player can
    drink 0--60 shots. Since each player can just play independently,
    this result extends to any number of players in BM8L.
  \item With two players, we know that BM5L (XXX check) does not allow
    all combinations of $\langle k_1, k_2 \rangle$ shots, though BM5L
    can achieve any $\langle k_1, k_2 \rangle$ where $\k_2 \in \{ 0, 1
    \}$. No other $k_2$ can be used universally, though of course many
    other combinations are possible
    (Figure~\ref{fig:compositeplayer2mock}).
  \item Open: Can BM6L achieve all $\langle k_1, k_2 \rangle$? Seems
    unlikely, based on how many samples we need to get close to 100\%
    for BM7L.
  \item Open: Can BM7L achieve all $\langle k_1, k_2 \rangle$? Seems
    likely, given how close BM7L is for a single player. We know it
    can get 96.67\%, at least!
  \item With three players one player can drink any number of shots in
    BMML with two other players helping.
\end{enumerate}

>>>>

Now we execute programs as before, and hope that we never encounter a
situation where we depend on a rule. If we finish without ever using
one of the \any\ rules, we evaluated a potentially large group of
configurations all at once. During the execution of a configuration,
if we need to use a rule that is currently marked \any, we explore all
of the possibilities for that spot. This is accomplished by a loop
that looks like the following (in Pseudo SML):

@@

% XXX TODO: Display in 3D cube.
It is also feasible overnight to enumerate all three-player games. The
results are three-dimensional, of course, but we can display the
outcomes for two of the players in the familiar presentation
(Figure~\ref{fig:3and2}). Note that $\langle k_1, k_2, k_3 \rangle$ is
achievable for any $k_1 \in \{ 0 .. 60 \}$, $k_2 \in \{ 0, 1, 2 \}$,
and some unknown $k_3$ (projected out of this display). This is a
significant improvement over what was achievable in BMML with two
players. It suggests that with enough friends willing to follow a
program, some set of people are likely to be able to achieve any
amount of drinks between them (if they have the ability to construct
the right rule set!); see Section~\ref{sec:conjectures}.

The sheer number of configurations for 4 or more players makes these
exact enumeration techniques infeasible. However, we have other
avenues for generalization (and exploration), which are investigated
in the next chapter.

@@

\begin{figure}
\begin{center}
\includegraphics[width=\linewidth]{soloncups.pdf}
\end{center}\vspace{-0.1in}
\caption{Possible outcomes for BM$n$L with a single player. With no
  cup states, it is only possible to drink nothing. By convention, the
  0\th\ cup is the special ``filled'' state, so it is only possible to
  drink on every turn (60) or never (0). As we add more cup states,
  the number of achievable states strictly increases; with 8 cup states
  we can drink any amount. 7 and 53 drinks are the most difficult to
  achieve, and can only be done with 8 cup states.
}
\label{fig:soloncups}
\end{figure}

@@

\begin{enumerate}
  \item With one player, we have exact bounds on what is possible in
    the generalized case. With 8 cup states, a single player can
    drink 0--60 shots. Since each player can just play independently,
    this result extends to any number of players in BM8L.
  \item With two players, we know that BM5L (XXX check) does not allow
    all combinations of $\langle k_1, k_2 \rangle$ shots, though BM5L
    can achieve any $\langle k_1, k_2 \rangle$ where $k_2 \in \{ 0, 1
    \}$. No other $k_2$ can be used universally, though of course many
    other combinations are possible
    (Figure~\ref{fig:composite2player}).
  \item Open: Can BM6L achieve all $\langle k_1, k_2 \rangle$? Seems
    unlikely, based on how many samples we need to get close to 100\%
    for BM7L.
  \item Open: Can BM7L achieve all $\langle k_1, k_2 \rangle$? Seems
    possible, given how close BM7L is for a single player. We know it
    can get 99.79\%, at least!
  \item With three players one player can drink any number of shots in
    BMML with two other players helping.
\end{enumerate}
